Quality Metrics for SKOS Vocabularies

### 2012-03-12 analysis.tex
added table statistics data

Our syntactical checks showed that only the Agrovoc vocabulary contained invalid datatypes and characters. After some minor syntax modifications, which don’t influence the evaluation against our criteria, we were also able to include this vocabulary. We also informed the AGROVOC team about this problem, which will try to fix it.

\begin{table}[h]
\caption{Analyzed vocabularies}
\begin{tabular}{|p{2cm}|p{6cm}|p{1.5cm}|p{.8cm}|p{.8cm}|p{.8cm}|p{.8cm}|p{.8cm}|}
\hline
\textbf{Domain} & \textbf{Vocabulary} & \textbf{CO} & \textbf{LR} & \textbf{SR} & \textbf{AR} & \textbf{CS} & \textbf{CL}\\
\hline
Media & Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & & & & & & \\
\hline
Science & Geonames Ontology &&&&&& \\
\hline
& Medical Subject Headings (MeSH) &&&&&& \\
\hline
& Peroxisome Knowledge Base &&&&&& \\
\hline
Government & Eurovoc &&&&&& \\
\hline
& Integrated Public Sector Vocabulary (IPSV) &&&&&& \\
\hline
Publications & Agrovoc &&&&&& \\
\hline
& DBpedia Categories &&&&&& \\
\hline
& University of Southampton Pressinfo &&&&&& \\
\hline
& New York Times People &&&&&& \\
\hline
& Library of Congress Subject Headings (LCSH) &&&&&& \\
\hline
Cross-domain & Meketre &&&&&& \\
\hline
Economy & Thesaurus for Economics (STW) &&&&&& \\
\hline
& North American Industry Classification System (NAICS) &&&&&& \\
\hline
Military & Thesaurus Landesverteidigungsakademie (LVAk) &&&&&&
\\
\hline
\end{tabular}
\label{vocabs}
\end{table}

>>>>

Our syntactical checks showed that only the AGROVOC vocabulary contained invalid datatypes and characters. After some minor syntax modifications, which don’t influence the evaluation against our criteria, we were also able to include this vocabulary. We also informed the AGROVOC team about this problem, which will try to fix it.

\begin{table}[h]
\caption{Analyzed vocabularies}
\begin{tabular}{lp{5cm}cccccc}
\textbf{Domain} & \textbf{Vocabulary} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Lexical Rel.}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
\toprule
Media & Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & 171991 & 178776 & 50892 & 343980 & 9 & 0 \\
\hline
Science & Geonames Ontology & 671 & 671 & 0 & 671 & 9 & 0 \\
\hline
& Medical Subject Headings (MeSH) & 24626 & 150617 & 38858 & 0 & 0 & 0 \\
\hline
& Peroxisome Knowledge Base & 2112 & 3628 & 2695 & 1716 & 1 & 0 \\
\hline
Government & Eurovoc & 6797 & 457788 & 18491 & 15512 & 128 & 0 \\
\hline
& Integrated Public Sector Vocabulary (IPSV) & 4732 & 7945 & 13843 & 4483 & 3 & 0 \\
\hline
Publications & Agrovoc & 31993 & 572138 & 63936 & 32043 & 1 & 0 \\
\hline
& DBpedia Categories & 743410 & 740352 & 1490316 & 0 & 0 & 0 \\
\hline
& University of Southampton Pressinfo & 1125 & 0 & 0 & 0 & 0 & 0 \\
\hline
& New York Times People & 4979 & 4979 & 0 & 4979 & 1 & 0 \\
\hline
& Library of Congress Subject Headings (LCSH) & 459182 & 746076 & 595754 & 815816 & 19 & 0 \\
\hline
Cross-domain & Meketre & 422 & 569 & 1698 & 6 & 2 & 0 \\
\hline
Economy & Thesaurus for Economics (STW) & 6524 & 31189 & 57907 & 6531 & 1 & 0 \\
\hline
& North American Industry Classification System (NAICS) & 4175 & 0 & 8684 & 2235 & 1 & 0 \\
\hline
Military & Thesaurus Landesverteidigungsakademie (LVAk) & 13411 & 17250 & 16346 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}
\label{vocabs}
\end{table}

### 2012-03-12 introduction.tex
added table statistics data

% What does "quality" mean in this context?
Each vocabulary reflects domain- and application-specific needs and vocabulary designers usually apply their own guidelines and rules (cf.,~\cite{Coronado2009}\todo{CM}{is this correct?}) to meet certain quality requirements. However, these requirements can differ across domains and lead to quality problems when a vocabulary is used in other environments. As a consequence, currently available vocabularies are, even though they are expressed in SKOS, often heterogeneous in terms of quality. The following examples illustrate that this can affect their applicability for tasks like query expansion, faceted browsing, clustering, or auto-completion:

@@

The SKOS specification doesn't make any explicit statements about vocabulary quality. It defines a set of \textbf{integrity conditions} that state ``whether or not given data are consistent with respect to the SKOS data model'' [\todo{SKOS reference}]. Existing quality checking tools, such as the PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}} or SKOSify\footnote{\url{http://code.google.com/p/skosify/}} can be used to verify that a given vocabulary fulfills these conditions. However, these conditions fail to capture \textbf{quality criteria} such as those mentioned in the examples before; criteria that go beyond the SKOS data model. Such criteria might be part of design rules and guidelines, but rely on \textbf{human judgement}, which is subjective and does not scale for larger, possibly linked Web vocabularies.

>>>>

% What does "quality" mean in this context?
Each vocabulary reflects domain- and application-specific needs and vocabulary designers usually apply their own guidelines and rules (cf.,~\cite{Coronado2009} who utilize a combination of automated and manual checks and reviews) to meet certain quality requirements. However, these requirements can differ across domains and lead to quality problems when a vocabulary is used in other environments. As a consequence, currently available vocabularies are, even though they are expressed in SKOS, often heterogeneous in terms of quality. The following examples illustrate that this can affect their applicability for tasks like query expansion, faceted browsing, clustering, or auto-completion:

@@

The SKOS specification doesn't make any explicit statements about vocabulary quality. It defines a set of \textbf{integrity conditions} that state ``whether or not given data are consistent with respect to the SKOS data model''\footnote{\url{http://www.w3.org/TR/skos-reference/}}. Existing quality checking tools, such as the PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}} or SKOSify\footnote{\url{http://code.google.com/p/skosify/}} can be used to verify that a given vocabulary fulfills these conditions. However, these conditions fail to capture \textbf{quality criteria} such as those mentioned in the examples before; criteria that go beyond the SKOS data model. Such criteria might be part of design rules and guidelines, but rely on \textbf{human judgement}, which is subjective and does not scale for larger, possibly linked Web vocabularies.
